Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-23 paper/paper.Rmd
fix paper issues related to anomaly bug identified #1

# Forecast dates + locations with anomalies
exclusions <- metadata |>
  DT(, .(forecast_date, location, anomaly)) |>
  unique() |>
  DT(, .(total = .N, exclude = sum(anomaly), include = .N - sum(anomaly))) |>
  DT(, per := round(exclude / total * 100, 1))

@@

# Number of forecast dates
forecast_dates <- metadata |>
  DT(, unique(forecast_date))

# Models per forecast date
models_per_forecast <- metadata |>
  summarise_forecasts_by(by = "forecast_date")

@@

locs_per_model_single_date <- metadata |>
    summarise_forecasts_by(
      var = "location", by = c("model", "forecast_date")
    ) |>
    DT(, unique(.SD[n == max(n), .(n)]), by = "model")

locs_per_model_date <- metadata |>
  summarise_forecasts_by(
    var = "location", by = c("model", "forecast_date")
  ) |>
  DT(locs_per_model_single_date[, .(model, max_n = n)], on = "model") |>
  DT(, n_per := n / max_n) |>
  DT(, .SD[!all(n == max_n)], by = "model")

models_per_loc_date <- metadata |>
  summarise_forecasts_by(var = "model", by = c("forecast_date", "location"))

@@

# Models coverage of forecast dates
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "forecast_date", by = "model") |>
  DT(order(n)) |>
  DT(, n_per := n / forecast_dates) |>
  DT(, type := fcase(
      model %in% global_models, "global",
      model %in% local_models, "local",
      model %in% partial_models[, model], "partial",
      default = "other"
    )
  )
```

>>>>

# Forecast dates + locations with anomalies
exclusions <- metadata |>
  DT(, .(target_end_date, location, anomaly)) |>
  unique() |>
  DT(, .(total = .N, exclude = sum(anomaly), include = .N - sum(anomaly))) |>
  DT(, per := round(exclude / total * 100, 1))

@@

# Number of forecast dates
forecast_dates <- metadata |>
  DT(, uniqueN(target_end_date))

# Models per forecast date
models_per_forecast <- metadata |>
  summarise_forecasts_by(by = "target_end_date")

@@

locs_per_model_single_date <- metadata |>
    summarise_forecasts_by(
      var = "location", by = c("model", "target_end_date")
    ) |>
    DT(, unique(.SD[n == max(n), .(n)]), by = "model")

locs_per_model_date <- metadata |>
  summarise_forecasts_by(
    var = "location", by = c("model", "target_end_date")
  ) |>
  DT(locs_per_model_single_date[, .(model, max_n = n)], on = "model") |>
  DT(, n_per := n / max_n) |>
  DT(, .SD[!all(n == max_n)], by = "model")

models_per_loc_date <- metadata |>
  summarise_forecasts_by(var = "model", by = c("target_end_date", "location"))

@@

# Models coverage of forecast dates
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "target_end_date", by = "model") |>
  DT(order(n)) |>
  DT(, n_per := n / forecast_dates) |>
  DT(, type := fcase(
      model %in% global_models, "global",
      model %in% local_models, "local",
      model %in% partial_models[, model], "partial",
      default = "other"
    )
  )
```
